\documentclass{pike-resume}



\begin{document}

\titlebar{Jonathan Pike}{Toronto, ON \\ \hfill \href{mailto: jonathan.d.s.pike@gmail.com}{jonathan.d.s.pike@gmail.com} \\ \hfill \href{https://jonathanpike.net}{https://jonathanpike.net}}

\hspace{2em} \textit{\large I love the web and want to make it better by building great things.}

\bluerule

\vspace{1em}

\begin{tabularx}{\textwidth}{p{.3\textwidth}X}
\textbf{\large Experience}	&  \rtitle{Full Stack Rails Developer}{May 2016 - Present} \\
  			   		& \textit{BioConnect} \\
					& \\
   					& Currently building \href{https://teamworks.cloud}{TeamWorks}, a time and attendance application for small to medium businesses. \\  
					& \\
 					& \textbf{My Accomplishments:}\\  
 			        		& \begin{itemize}
                                      	\item Lead the development of a dashboard for internal teams to provide insight into app usage and inform future product 	development using \href{https://vuejs.org}{Vue.js} in a Rails Engine.
                                    	\item Eliminated manual sales processes by creating an onboarding process for new customers and integrated with \href{http://stripe.com/}{Stripe} for online payments.
                                    	\item Chief architect of the new timecards and scheduling modules, implementing Rails conventions for easier maintenance.
                                    	\item Developed a testing protocol and built a test suite using Minitest and Capybara. Configured GitLab CI to run the test suite with each commit.
          				\end{itemize} \\
					& \bluerule \\     
					& \\  				
	        			         & \rtitle{Wills and Estates Law Clerk}{Nov 2011 - May 2016} \\
                                          & \textit{Sanguinetti + associates} \\
                                          & \\
                                          & With no prior training, I obtained a level of professionalism and proficiency in just 6 months at this boutique legal practice, preparing Wills, Powers of Attorney, and a variety of Court documents for Estate Administration. \\  
                                          & \\
                                          & \textbf{My Responsibilities:}\\  
                                          & \begin{itemize}
                                           \item Practiced effective time management and multitasking to guarantee timely completion of work, meeting deadlines and maintaining high quality of work.
                                           \item Communicated with clients in a professionally friendly manner on a day-to-day basis in person and over the phone, ensuring customer satisfaction.
                                            \item Drafted and proofread legal documents of varying complexity, unsupervised and with minimal instruction, demonstrating excellent attention to detail.
                                            \end{itemize}
\end{tabularx}
				
\bluerule

\vspace{1em}

\begin{tabularx}{\textwidth}{p{.3\textwidth}X}
\textbf{\large Education and Professional Development} & \rtitle{Programming Bootcamp}{Sept - Dec 2015} \\
                                                                                         & The Firehose Project \\
                                                                                         & \\
                                                                                         & Became a capable software developer in this intensive 15-week program, able to break complex problems into more manageable problems. I gained experience with the following tools of the trade: \\  
                                                                                         & \\
                                                                                         & \begin{itemize}
                                                                                          	\item Built basic CRUD Rails apps following standard Rails conventions (without using scaffolding), involving mailers, validations, image uploading on AWS S3, and nested RESTful routes.
                                                                                        	\item Implemented tests with Minitest?s Test::Unit syntax for unit and functional tests.
                                                                                        	\item Worked through traditional computer science algorithms and data structure challenges:
                                                                                        	\begin{itemize}
                                                                                        		\item Graph search (depth-first \& breadth-first).
                                                                                        		\item Linked lists with basic Ruby classes.
                                                                                        		\item Stacks and queues in Ruby.
                                                                                        		\item Reversed linked lists (both with a recursive solution with mutation, and a solution that leverages stack-like properties of linked lists).
                                                                                        		\item Floyd?s algorithm (tortoise \& hare) to detect cycles within a linked list.
                                                                                        	\end{itemize}
                                                                                          \end{itemize} \\
                                                                                          & \bluerule \\
										      & \\                                                                        
                                                                                         & \rtitle{Capstone Project}{Nov - Dec 2015} \\
                                                                                         & The Firehose Project \\
                                                                                         & \\
                                                                                         & Built a Ruby on Rails chess web application, working on a remote team of 5 developers, that enforces the rules of chess, including preventing users moving into check and support for \href{https://en.wikipedia.org/wiki/Castling}{castling} and \href{https://en.wikipedia.org/wiki/En_passant}{en passant}. \href{https://github.com/teamendgame/endgame-chess}{View the GitHub repository} and \href{http://endgame-chess.herokuapp.com/}{the app running in production on Heroku}. \\  
                                                                                         &\\
                                                                                         & \textbf{My Accomplishments:}\\
                                                                                         & \begin{itemize}
                                                                                          	\item Wrote the business logic for determining if the game is in the state of \href{https://github.com/teamendgame/endgame-chess/pull/41/files}{check} and \href{https://github.com/teamendgame/endgame-chess/pull/67}{checkmate}.
                                                                                        	\item Uncovered, tracked down, and resolved several bugs in both our Ruby and Javascript code, including an intermittent bug that prevented movement of some pieces. See \href{https://github.com/teamendgame/endgame-chess/pull/63}{Pull Request 1} and \href{https://github.com/teamendgame/endgame-chess/pull/77}{Pull Request 2} on GitHub.
                                                                                        	\item Followed test-driven development, Agile and SCRUM methodologies, and had frequent code reviews and pair programming sessions. 
                                                                                        	\item Held accountable for my performance by Travis Johnson, a devops engineer at \href{http://www.truex.com/}{true[X]}, who led the team.
                                                                                        \end{itemize} \\
                                                                                        & \bluerule \\
                                                                                        & \\
                                                                                        & \rtitle{Honours Bachelor of Arts with Distinction}{2006 - 2010} \\
                                                                                        & University of Toronto \\
                                                                                        &\\
                                                                                        & Double Major: Management and Political Science \\
                                                                                        & \\
                                                                                        & GPA: 3.30 \\
                                                                                        & \bluerule \\
                                                                                        & \\
                                                                                        & \rtitle{Mathematical and Computational Sciences Honour Roll}{2009 - 2010} \\
										    & University of Toronto \\
										
\end{tabularx}

\bluerule

\vspace{1em}

\begin{tabularx}{\textwidth}{p{.3\textwidth} p{.3\textwidth} p{.3\textwidth}}
\textbf{\large Technical Skills} & \textbf{What I know} & \textbf{What I'm learning} \\
& Ruby, Rails; Javascript, Coffeescript; HTML; CCS3, Sass; Postgresql; Git
& Go 
\end{tabularx}
\end{document} 